---
title: "SOLE 2015 Posters as a picture"
author: "Lars Vilhuber"
output:
  pdf_document:
    toc: yes
  html_document:
    keep_md: yes
---

======================
```{r libraries,echo=FALSE,cache=FALSE,message=FALSE}
library(data.table)
library(tm)
library(wordcloud)
library(knitr)
```

```{r readin,echo=FALSE,message=FALSE,cache=TRUE}

# Source: titles of all published papers
#tmp2 <- read.delim("ceswp_1988_to_2013.rdf.txt", sep="",header = FALSE)
#tmp <- read.delim("ceswp_1988_to_2013.rdf.txt", sep=":",header = FALSE)
tmp <- fread("iconv -t UTF8 -c < ceswp_1988_to_2013.rdf.txt | grep -e '^Abstract:' | sed 's/^Abstract:/Abstract|/'", sep="|",header = FALSE)

accepted <- tmp[tmp$V1=="Abstract",]
```


```{r parse,echo=FALSE,message=FALSE,cache=TRUE}
doc.vec <- VectorSource(t(accepted))
doc.corpus <- Corpus(doc.vec)
doc.corpus <- tm_map(doc.corpus, content_transformer(function(x) iconv(enc2utf8(x), sub = "byte")))
doc.corpus <- tm_map(doc.corpus, content_transformer(tolower))
#doc.corpus.nw <- tm_map(doc.corpus, stripWhitespace)
doc.corpus <- tm_map(doc.corpus, removePunctuation)
doc.corpus <- tm_map(doc.corpus, removeNumbers) 
doc.corpus <- tm_map(doc.corpus, removeWords, stopwords("english"))
doc.corpus <- tm_map(doc.corpus, removeWords, c("the","abstract","paper","using"))

TDM <- TermDocumentMatrix(doc.corpus)
# find the most frequent word
m <- as.matrix(TDM)
v <- sort(rowSums(m),decreasing = TRUE)

try_max <- v[[1]]
try_five <- v[[5]]
restrict_num <- 30
top_100 <- v[[100]]
most_freq <- findFreqTerms(TDM,try_max)
#
```
Or: the power of **`r most_freq`**.

A picture is worth a thousand words. Or in this case `r nrow(as.data.frame(findFreqTerms(TDM, 1)))` words - the number of distinct words in titles of the `r nrow(accepted)` papers accepted.

```{r graph, echo=FALSE, fig.width=7, message=FALSE,cache=TRUE}
# graph the whole thing
palette <- brewer.pal(9,"PuBuGn")[-(1:4)]
# if producing the webpage, you need to comment out the following two lines
#myscale <- c(2,.1)
wordcloud(rownames(as.matrix(TDM)), rowSums(as.matrix(TDM)), min.freq = top_100, color = palette,random.order=FALSE)
```

To produce this graph, we downloaded the ReDif-formatted metadata for the CES Working Paper archive, and read in the Abstract field.
```{r, eval=FALSE, ref.label='readin'}
```
We then used the _R text mining library_  to clean and parse the titles:
```{r, eval=FALSE, ref.label='parse'}
```
which generated a "corpus" of documents.
```{r corpus,echo=FALSE}
#summary(doc.corpus)
```

In fact, we lied somewhat above: we did not show **`r nrow(as.data.frame(findFreqTerms(TDM, 1)))`** words, but rather, for the sake of clarity, restricted ourselves to the top 100 words. If we had instead wanted to show the 
**`r nrow(as.data.frame(findFreqTerms(TDM, restrict_num)))`** words with at least `r restrict_num` mentions in the (cleaned) corpus, we would have obtained the [following graph](graphing.CES_n`r restrict_num`.png):

```{r graph_all_titles, fig.width=7, message=FALSE,warning=FALSE,echo=FALSE,fig.keep='high',cache=TRUE}
#myscale <- c(2,.1)
wordcloud(rownames(as.matrix(TDM)), rowSums(as.matrix(TDM)), min.freq = restrict_num, color = palette, rot.per = 0.3,random.order=FALSE)
```
```{r graph3, message=FALSE,warning=FALSE,echo=FALSE,cache=TRUE}
png(paste("graphing.CES_n",restrict_num,".png",sep = ""),height=1600,width=1600,res=600)
myscale <- c(2,.1)
wordcloud(rownames(as.matrix(TDM)), rowSums(as.matrix(TDM)), scale=myscale, min.freq = restrict_num, color = palette, rot.per = 0.3,random.order=FALSE)
message <- try(dev.off(),silent=TRUE)
myscale <- c(5,.1)
png(paste("graphing.CES_n",restrict_num,".HIRES1.png",sep = ""),height=1600,width=1600,res=300)
wordcloud(rownames(as.matrix(TDM)), rowSums(as.matrix(TDM)), scale=myscale, min.freq = restrict_num, color = palette, rot.per = 0.3,random.order=FALSE)
message <- try(dev.off(),silent=TRUE)
```

For the curious, while the most frequent word is **`r findFreqTerms(TDM,try_max)`**, the top **`r nrow(as.data.frame(findFreqTerms(TDM,try_five)))`** are:
```{r topfive, echo=FALSE,cache=TRUE,message=FALSE}
t<-as.data.frame(head(v,5))
names(t)<-c("Frequency")
kable(t)
```



*******************
 * The code behind this endeavor is available at [github.com/larsvilhuber/ceswp-wordart](https://github.com/larsvilhuber/ceswp-wordart)
 * This document was produced using
```{r environment, echo=TRUE}
R.Version()
Sys.info()
```
